---
output:
  pdf_document: default
  word_document: default
  html_document: default
---
```{r}
#Exercise 2.3. The data set UCBAdmissions is a 3-way table of frequencies classified by Admit, Gender, and Dept.
#(a)	Find the total number of cases contained in this table.
library(datasets)
```

```{r}
View(UCBAdmissions)
```

```{r}
#str function: 0 To see the structure of matrices and its attibutes we use str().
str(UCBAdmissions)
```

```{r}
summary(UCBAdmissions)
```
#Summary: - The summary method for tables produces a simple chi-square test of independence of all factors.
#for example :- Number of factors in UCBAdmissions dataset is 3, chi-square is 2000.3, degree of freedom is 16 and p-value is 0 which indicates a statistically significant difference between groups because p-value (probability) is less than 0.05.

```{r}
#(b)	For each department, find the total number of applicants.
margin.table(UCBAdmissions, 3)
```
#Ans:- We use margin.table(UCBAdmissions, 3) to sum a table UCBAdmission for the indices in margin (3), that is, over the dimensions not included in margin. 
```{r}
#(c)	For each department, find the overall proportion of applicants who were admitted.
n=24
Admit <- factor(sample(c("Admitted","Rejected"), n, rep=TRUE))
mydata = data.frame(Admit)
mydata
```

```{r}
table(mydata$Admit)
```

```{r}
mydata1 = UCBAdmissions[,1,] + UCBAdmissions[,2,]
mydata1
```

```{r}
prop.table(mydata1[,1])
```

```{r}
prop.table(mydata1[,2])
```

```{r}
prop.table(mydata1[,3])
```

```{r}
prop.table(mydata1[,4])
```

```{r}
prop.table(mydata1[,5])
```

```{r}
prop.table(mydata1[,6])
```

```{r}
prop.table(ftable(UCBAdmissions, row.vars = "Admit", col.vars = "Dept"))
```
#In above result, every row, the proportions sum up to 1. Now you can see that 13 percent of the people showing admitted who were in department A.
#ftable:-For 3-way and larger tables, the functions ftable()provide a convenient and flexible tabular display.
#prop.table: -For tables of proportions, use the prop.table()function.
```{r}
#(d)	Construct a tabular display of department (rows) and gender (columns), showing the proportion of #applicants in each cell who were admitted relative to the total applicants in that cell.
UCB <- aperm(UCBAdmissions, c(3,2,1))
UCB
```
#aperm function: - it permutes the dimensions when data are in table form.
```{r}
#Exercise 2.5. The data set UKSoccer in vcd gives the distributions of number of goals scored by the 20 teams #in the 1995/96 season of the Premier League of the UK Football Association.
#(a)	Verify that the total number of games represented in this table is 380.
library(vcd)
```

```{r}
data("UKSoccer")
```

```{r}
View(UKSoccer)
```

```{r}
summary(UKSoccer)
```
#for example :- Number of factors in UKScoccer dataset is 2, chi-square is 18.699, degree of freedom is 16 and p-value is 0.3 which indicates there is not a statistically significant difference between groups because p-value (probability) is more than 0.05.

```{r}
ftable(UKSoccer)
```

```{r}
#(b)	Find the marginal total of the number of goals scored by each of the home and away teams.
UK <- addmargins(UKSoccer, FUN = sum)
UK
```
#addmargins function: - It is used to show the sum of all the frequency values. addmargins(X, margin, FUN=sum), which extends the dimensions of a table or array with the marginal values calculated by FUN.

```{r}
#(c)	Express each of the marginal totals as proportions.
prop.table(UK)
```
#prop.table function: - It expresses the table entries as a fraction of a given marginal table.

```{r}
#(d)Comment on the distribution of the numbers of home-team and away-team goals. Is there any evidence that #home teams score more goals on average?
library(ggplot2)
```

```{r}
library(GGally)
```

```{r}
library(rlang)
```

```{r}
UK1 <- as.data.frame(UKSoccer)
class(UK1)
```

```{r}
names(UKSoccer)
```

```{r}
names(UK1) <- gsub("*Rate", "", names(UK1))
names(UK1)[1:2] <-  c("Away", "Home")
GGally::ggpairs(UK1[,c(1:3)], title = "correlation of home team and away team goals", diag = list(continuous = 'density'), axisLabels='none')
??enexprs
```
#Ans:- In above plot, there is an evidence that home teams score more goals on average based on box plots. The median of home games are more than away games.

```{r}
#Exercise2.7
#(a)	Try this the long way: convert UCBAdmissions to a data frame (as.data.frame()), manipulate the factors (e.g., interaction()), then convert back to a table (as.data.frame()).
UCB1 <- as.data.frame(UCBAdmissions)
head(UCB1)
```

```{r}
xtabs(Freq ~ Admit, data = UCB1)
```
#xtabs function: - This function allows us to create cross tabulations of data using formula style input. This typically works with case-form or frequency-form data supplied in a data frame or a matrix.

```{r}
UCB2 <- interaction(UCBAdmissions)
UCB2
```

```{r}
#as.data.frame function converts a data frame to a table.
UCB3 <- as.data.frame(UCB2)
UCB3
```

```{r}
#(b)	Try this the short way: both ftable() and structable() have as.matrix() methods that convert their result to a matrix.
ftable(UCBAdmissions)
```

```{r}
ftable(Admit + Gender ~ Dept, data=UCBAdmissions)
```
#In the above result, the ftable() function is used to print the results more attractively as a 2-way or flat table.
#from both frequency table, I am trying to show frequency of male/female who are admitted/rejected by departments. Overall in all department male admitted frequency is higher than female except department F. Also, in department F rejections frequency is higher than female.

```{r}
structable(UCBAdmissions)
```
#The structable() function is similar as ftable(), but more general, and uses recursive splits in the vertical or horizontal directions.

```{r}
#Exercise 2.8. The data set VisualAcuity in vcd gives a 4 × 4 × 2 table as a frequency data frame.
#(a)	From this, use xtabs() to create two 4 × 4 frequency tables, one for each gender.
library(vcd)
```
#install.packages("vcd")
#installed above package because VisualAcuity dataset is in "vcd" package.

```{r}
View(VisualAcuity)
```

```{r}
summary(VisualAcuity)
```
#In VisualAcuity dataset, frequency ranges from 27 to 1772. Median is lower than mean and 3rd quartile is just above mean. The IQR is 298.5. 

```{r}
str(VisualAcuity)
```
#The visualAcuity dataset having 32 observations and 4 attributes/columns. 

```{r}
A.tab <- xtabs(Freq~right+left+gender,data=VisualAcuity)
print(A.tab)
```
#I converted the VisualAcuity to a 3-way table using xtabs(), giving output as variable A.tab.

```{r}
#(b)	Use structable() to create a nicely organized tabular display.
structable(gender ~ right+left, data=VisualAcuity)
```
#
```{r}
#(c)	Use xtable() to create a LATEX or HTML table.
library(xtable)
data("VisualAcuity")
```
#By default, xtable() formats VisualAcuity in LATEXas a vertical table, and prints the LATEX markup shown below.

```{r}
xtable(VisualAcuity[1:24, ])
```




